---
title: "ISA 616 Project 2"
date: "`r format(Sys.time(), '%d %B, %Y')`"
author: "Samantha Erne and Amber Kopitke"
format:
  html:
    toc: true
    toc-location: left
    toc-expand: true
    code-tools: true 
    code-fold: true
    code-overflow: scroll
    self-contained: true
---

```{r setup, include=FALSE, warnings= FALSE, messages= FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.width=8, fig.height=6)
```

# Project Overview

In this project, we will be using data collected from 2019-2021 to visualize geographic trends of Farmer School of Business graduates. The clients for this project are Mr. Kirk Bogard and his staff in the FSB External Relations office. 

The Business Value Proposition that we created for this project is pictured below. In this BVP, we described our clients, their jobs, and how our solution will both kill their pains as well as provide additional gains to the clients. 

'''
BVP PHOTO
'''

## Data Description

The data that we will be using for this project is data collected from graduating FSB students in the classes of 2019, 2020, and 2021. This data includes information on major, job title, company, job location, salary, and much more. Analyzing this data will allow us to provide our clients with critical insights regarding the geographic trends of FSB graduates that will help them to prepare seniors for the job search and better place students in jobs.

Below is a snapshot of the data set before any cleaning has been done. 

```{r}
fsb_data <- readRDS("~/Desktop/ISA 616/GitHub/ISA616repo/ISA616-Project2-Group1/FSB_BI_Survey_2019_2021.rds")
head(fsb_data)
summary(fsb_data)
```

# Cleaning the Data

Before we can start analyzing the data, we need to clean it. Before we start cleaning the data, we want to summarize it to gain a better understanding of the data structure and any issues in the data.

## Reviewing Column Types

To start cleaning the data, we want to check and make sure that all columns are of the proper type. 

```{r}
sapply(fsb_data, class)
```

During our review of data types, we noticed some columns that we believe should have their type changed.

* `year.x` should be numeric not character

* `survey_offers` should be numeric not character

* `gender` should be factor not character (???)

* `IPEDS.Race.Ethnicity` should be factor not character (???)

## Review Column Values

* OH and Ohio and OHIO make one


## Checking for Missing Values

### Imputing Missing Values

```{r}
colSums(is.na(fsb_data))
```
